Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Updated Figure 8

hex_grid_coloured_scurve1 + 
  hex_grid_coloured_scurve2 + 
  hex_grid_coloured_scurve3 +
hex_grid_coloured_scurve1_dens +
  hex_grid_coloured_scurve2_dens +
  hex_grid_coloured_scurve3_dens +
  plot_layout(guides='collect', ncol = 3,
              heights = c(2,1)) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

>>>>

hex_grid_coloured_scurve1 + 
  hex_grid_coloured_scurve2 + 
  hex_grid_coloured_scurve3 +
  plot_layout(guides='collect', ncol = 3,
              heights = c(2,1)) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```
